---
title: "end_nodes"
output:
  pdf_document: default
  html_document: default
---


```{r}
source("../RajivFunctions.R")
source('get_nodes_new.R')
library(trajr)
library(dplyr)
```

```{r}
firstposs_moments_ball = full_game %>%
  filter(game_clock > 696, quarter == 1) %>%
  filter(lastname == "ball")

nodes <- get_nodes_new(1:nrow(firstposs_moments_ball))

```


```{r}
fullcourt() +
  geom_point(data = firstposs_moments_ball,
             aes(x_loc, y_loc, color = team)) + 
  geom_point(data = nodes,
             aes(x_loc, y_loc), color = "red") +
  scale_color_manual(values = c("Lakers" = "#fdb927",
                                "Clippers" = "#1D428A",
                                "ball" = "#FA8320")) +
  scale_y_reverse()
```

Given these nodes, we want to find the next spot when the ball stops moving. So for every row, find difference in total area 

```{r}
firstposs_moments_ball$area_diff <- 0

for (i in 1:nrow(firstposs_moments_ball)) {
  firstposs_moments_ball$area_diff[i] = 
    sqrt(((firstposs_moments_ball$x_loc[i+1] - firstposs_moments_ball$x_loc[i]) ** 2) +
               ((firstposs_moments_ball$y_loc[i+1] - firstposs_moments_ball$y_loc[i]) ** 2) +
                 ((firstposs_moments_ball$radius[i+1] - firstposs_moments_ball$radius[i]) ** 2))
}

firstposs_moments_ball$sig_mov <- firstposs_moments_ball$area_diff > 0.5
```


```{r}
endnodes_df <- NULL
for (i in 1:nrow(nodes)) {
  postnode_df <- firstposs_moments_ball[firstposs_moments_ball$game_clock < nodes$game_clock[i] - 0.08 &
                                          firstposs_moments_ball$quarter == nodes$quarter[i], ]
  endnode <- postnode_df[postnode_df$sig_mov == FALSE,][1,]
  endnodes_df <- rbind(endnodes_df, endnode)
}

```

```{r}
nodes$pass_num <- c(1:nrow(nodes))
endnodes_df$pass_num <- c(1:nrow(nodes))
```


```{r}
fullcourt() +
  geom_point(data = firstposs_moments_ball,
             aes(x_loc, y_loc, color = team)) + 
  geom_point(data = nodes,
             aes(x_loc, y_loc), color = "red", size = 3) +
  geom_text(data = nodes,
            aes(label=pass_num, x= x_loc, y = y_loc)) +
  geom_point(data = endnodes_df,
             aes(x_loc, y_loc), color = "green", size = 3) +
  geom_text(data = endnodes_df,
            aes(label=pass_num, x= x_loc, y = y_loc)) +
  scale_color_manual(values = c("Lakers" = "#fdb927",
                                "Clippers" = "#1D428A",
                                "ball" = "#FA8320")) +
  scale_y_reverse()
```

--------------------------------------------------------------------------------------------------------------
Compare get_nodes and get_nodes_new
Random Possession: 3rd quarter, start at 7:36 remaining


Now lets try it for a random set of times 

```{r}
randomposs_moments_ball = full_game %>%
  filter(game_clock < 462, game_clock > 430, quarter == 3) %>%
  filter(lastname == "ball")

nodes <- get_nodes(randomposs_moments_ball[1,]$frame_num:
                  randomposs_moments_ball[nrow(randomposs_moments_ball),]$frame_num)

```


```{r}
fullcourt() +
  geom_point(data = randomposs_moments_ball,
             aes(x_loc, y_loc, color = team)) + 
  geom_point(data = nodes,
             aes(x_loc, y_loc), color = "red") +
  scale_color_manual(values = c("Lakers" = "#fdb927",
                                "Clippers" = "#1D428A",
                                "ball" = "#FA8320")) +
  scale_y_reverse()
```

Given these nodes, we want to find the next spot when the ball stops moving 

1) for every row, find difference in total area 

```{r}
randomposs_moments_ball$area_diff <- 0

for (i in 1:nrow(randomposs_moments_ball)) {
  randomposs_moments_ball$area_diff[i] = 
    sqrt(((randomposs_moments_ball$x_loc[i+1] - randomposs_moments_ball$x_loc[i]) ** 2) +
               ((randomposs_moments_ball$y_loc[i+1] - randomposs_moments_ball$y_loc[i]) ** 2) +
                 ((randomposs_moments_ball$radius[i+1] - randomposs_moments_ball$radius[i]) ** 2))
}

randomposs_moments_ball$sig_mov <- randomposs_moments_ball$area_diff > 0.5
head(randomposs_moments_ball)

```


```{r}
endnodes_df <- NULL
for (i in 1:nrow(nodes)) {
  postnode_df <- randomposs_moments_ball[randomposs_moments_ball$game_clock < nodes$game_clock[i] - 0.08 & randomposs_moments_ball$quarter == nodes$quarter[i], ]
  endnode <- postnode_df[postnode_df$sig_mov == FALSE,][1,]
  endnodes_df <- rbind(endnodes_df, endnode)
}

```

```{r}
nodes$pass_num <- c(1:nrow(nodes))
endnodes_df$pass_num <- c(1:nrow(nodes))
```


```{r}
fullcourt() +
  geom_point(data = randomposs_moments_ball,
             aes(x_loc, y_loc, color = team)) + 
  geom_point(data = nodes,
             aes(x_loc, y_loc), color = "red", size = 3) +
  geom_text(data = nodes,
            aes(label=pass_num, x= x_loc, y = y_loc)) +
  geom_point(data = endnodes_df,
             aes(x_loc, y_loc), color = "green", size = 3) +
  geom_text(data = endnodes_df,
            aes(label=pass_num, x= x_loc, y = y_loc)) +
  scale_color_manual(values = c("Lakers" = "#fdb927",
                                "Clippers" = "#1D428A",
                                "ball" = "#FA8320")) +
  scale_y_reverse()
```




-----------------------------------------




Now lets try it for a random set of times 

```{r}
randomposs_moments_ball = full_game %>%
  filter(game_clock < 462, game_clock > 430, quarter == 3) %>%
  filter(lastname == "ball")

nodes <- get_nodes_new(randomposs_moments_ball[1,]$frame_num:
                  randomposs_moments_ball[nrow(randomposs_moments_ball),]$frame_num)

```


```{r}
fullcourt() +
  geom_point(data = randomposs_moments_ball,
             aes(x_loc, y_loc, color = team)) + 
  geom_point(data = nodes,
             aes(x_loc, y_loc), color = "red") +
  scale_color_manual(values = c("Lakers" = "#fdb927",
                                "Clippers" = "#1D428A",
                                "ball" = "#FA8320")) +
  scale_y_reverse()
```

Given these nodes, we want to find the next spot when the ball stops moving 

1) for every row, find difference in total area 

```{r}
randomposs_moments_ball$area_diff <- 0

for (i in 1:nrow(randomposs_moments_ball)) {
  randomposs_moments_ball$area_diff[i] = 
    sqrt(((randomposs_moments_ball$x_loc[i+1] - randomposs_moments_ball$x_loc[i]) ** 2) +
               ((randomposs_moments_ball$y_loc[i+1] - randomposs_moments_ball$y_loc[i]) ** 2) +
                 ((randomposs_moments_ball$radius[i+1] - randomposs_moments_ball$radius[i]) ** 2))
}

randomposs_moments_ball$sig_mov <- randomposs_moments_ball$area_diff > 0.5
head(randomposs_moments_ball)

```


```{r}
endnodes_df <- NULL
for (i in 1:nrow(nodes)) {
  postnode_df <- randomposs_moments_ball[randomposs_moments_ball$game_clock < nodes$game_clock[i] - 0.08 & randomposs_moments_ball$quarter == nodes$quarter[i], ]
  endnode <- postnode_df[postnode_df$sig_mov == FALSE,][1,]
  endnodes_df <- rbind(endnodes_df, endnode)
}

```

```{r}
nodes$pass_num <- c(1:nrow(nodes))
endnodes_df$pass_num <- c(1:nrow(nodes))
```


```{r}
fullcourt() +
  geom_point(data = randomposs_moments_ball,
             aes(x_loc, y_loc, color = team)) + 
  geom_point(data = nodes,
             aes(x_loc, y_loc), color = "red", size = 3) +
  geom_text(data = nodes,
            aes(label=pass_num, x= x_loc, y = y_loc)) +
  geom_point(data = endnodes_df,
             aes(x_loc, y_loc), color = "green", size = 3) +
  geom_text(data = endnodes_df,
            aes(label=pass_num, x= x_loc, y = y_loc)) +
  scale_color_manual(values = c("Lakers" = "#fdb927",
                                "Clippers" = "#1D428A",
                                "ball" = "#FA8320")) +
  scale_y_reverse()
```

The 6th pass, which seems like it should be pretty clear that it is a pass, is not showing. Something to look into.


-----------------------------------------

