---
title: "get shots rmd"
output: html_document
---
```{r}
source("get_shots.R")
source("get_nodes_new.R")
source("../RajivFunctions.R")
library(trajr)
library(dplyr)
```

```{r}
all_nodes <- final_nodes()
all_all <- final_nodes_shots()
all_nodes
all_all
```

```{r}
library(hms)
all_ball_frames2$game_clock = hms::as_hms(game_clock)

full_game2 = read.csv("full_game.csv")
all_ball_frames2 = full_game2[full_game2$lastname == "ball", ]
all_ball_frames2$game_clock = hms::as_hms(all_ball_frames2$game_clock)
```


```{r}
for (i in 1:nrow(all_ball_frames2)) {
  all_ball_frames2$minute[i] = strsplit(as.character(all_ball_frames2$game_clock[i]), ":")[[1]][2]
}
```


What defines a shot:
1) diff > 0.1 seconds -> a new shot
2) find closest 7 feet ball point 


```{r}
all_ball_above10 <- all_ball_frames2[all_ball_frames2$radius > 10,]

shotnum = 1
for(i in 1:(nrow(all_ball_above10) - 1)) {
  all_ball_above10$time_diff[i] <-
    all_ball_above10$game_clock[i] - 
    all_ball_above10$game_clock[i + 1]
  if(all_ball_above10$time_diff[i] > 0.06) {
    shotnum = shotnum + 1
  }
  all_ball_above10$shot_num[i] = shotnum
}

all_ball_new = merge(all_ball_above10, all_ball_frames2, 
      by = colnames(all_ball_frames2), 
      all = TRUE)

max(all_ball_new$shot_num, na.rm = TRUE)
```

```{r}
all_ball_new <- all_ball_new[order(all_ball_new[,12],
                                   -all_ball_new[,10]), ]
```

finds first occurance of shot
goes backwards until it finds a y_loc under 7 feet 
marks it and everything up to it as shot number 

```{r}
shot_dummy = 1
for(i in 1:nrow(all_ball_new)) {
  if (!is.na(all_ball_new$shot_num[i]) &
      all_ball_new$shot_num[i] == shot_dummy) {
    for(j in i:0) {
      if (all_ball_new$radius[j] > 7) {all_ball_new$shot_num[j] = shot_dummy}
      else {break}
    }
    shot_dummy = shot_dummy + 1 
  }
}
```

find last point where a shot is marked (last point where the ball is 10 feet, presumably when its going down the rim)

```{r}
shot_end_time = 
  all_ball_new[!is.na(all_ball_new$shot_num),] %>%
  group_by(shot_num) %>%
  summarize(shot_end_time = min(game_clock),
            num_frames = n())

ggplot(shot_end_time, aes(num_frames)) +
  geom_histogram()
```

insert text

```{r}
all_shot_starts = 
  all_ball_new %>%
  group_by(shot_num) %>%
  slice(1)

all_shot_starts = all_shot_starts[!(all_shot_starts$shot_clock == 0) &
                                    !is.na(all_shot_starts$shot_clock), ]
all_shot_starts = all_shot_starts[!(all_shot_starts$frame_num == 1), ]

all_shot_starts = all_shot_starts[!(all_shot_starts$radius > 8),]

```

```{r}
all_shot_starts <- merge(all_shot_starts, shot_end_time, by = "shot_num")
all_shot_starts$shot_end_time = as.numeric(all_shot_starts$shot_end_time)
```


load real shot data

```{r}
shots_nbastatr <- read.csv("shots_nbastatr.csv")
shots_nbastatr <- shots_nbastatr[order(shots_nbastatr$idEvent),]
```


create unique time variable for each data frame

```{r}
for (i in 1:nrow(shots_nbastatr)) {
  shots_nbastatr$time[i] <- (shots_nbastatr$minutesRemaining[i] * 60) +
                            (shots_nbastatr$secondsRemaining[i])
  shots_nbastatr$time[i] = shots_nbastatr$time[i] + ((4 - shots_nbastatr$numberPeriod[i]) * 720)
}

for (i in 1:nrow(all_shot_starts)) {
  all_shot_starts$time[i] <- as.numeric(all_shot_starts$game_clock[i])
  all_shot_starts$time[i] = all_shot_starts$time[i] + ((4 - all_shot_starts$quarter[i]) * 720)
  all_shot_starts$shot_end_time[i] = all_shot_starts$shot_end_time[i] + ((4 - all_shot_starts$quarter[i]) * 720)
}

test <- all_shot_starts$time - all_shot_starts$shot_end_time


all_ball_new[!is.na(all_ball_new$shot_num), ]
```


put the data together 

```{r}
count = 0
track_rows <- c()
nbastatr_rows <- c()
for (i in 1:nrow(all_shot_starts)) {
  for (j in 1:nrow(shots_nbastatr)) {
    if (abs(all_shot_starts$shot_end_time[i] - shots_nbastatr$time[j]) < 3) {
      count = count + 1
      track_rows <- append(track_rows, i)
      nbastatr_rows <- append(nbastatr_rows, j)
    }
  }
}

all_shot_starts
all_shot_starts$shot_total_time = all_shot_starts$time - all_shot_starts$shot_end_time

```

